Minimum Regret Search for Single- and Multi-Task Optimization

### 2016-05-23 2016_ICML/cmrs.tex
Final version

\subsection{Formulation}
Let $\mathcal{X} \subset \mathcal{R}^D$ be some bounded domain and $f: \mathcal{X} \mapsto
\mathbb{R}$ be a function. We are interested in finding the maximum
$\mathbf{x}^\star$ of $f$ on $\mathcal{X}$. Let there be a probability measure
$p(f)$ over the space of functions $f: \mathcal{X} \mapsto \mathbb{R}$, such as
a GP. Based on this $p(f)$, we would ultimately like to
select an $\mathbf{\tilde x}$ which has minimum simple regret
$R_f(\mathbf{\tilde x})$. We define the expected simple regret ER of
selecting parameter $\mathbf{x}$ under $p(f)$ as follows:
$$\text{ER}(p)(\mathbf{x}) = \mathbb{E}_{p(f)}[R_f(\mathbf{x})]
= \mathbb{E}_{p(f)}[\max_{\mathbf{x}} f(\mathbf{x}) - f(\mathbf{
x})]$$

In $N$-step BO, we are given a budget of $N$ function evaluations and are to choose a sequence of $N$ query points
$X^q_N=\{\mathbf{x}^q_1, \dots, \mathbf{x}^q_N\}$ for which we evaluate $y_i = f(\mathbf{x}^q_i) +
\epsilon$ to obtain $\mathcal{D}_N = \{\mathbf{x}^q_i, y_i\}_{i=1}^N$. Based on this, 
 $p_N(f) = p(f \vert \mathcal{D}_N)$ is estimated and a point
$\mathbf{\tilde x}_N$ is recommended as the estimate of $\mathbf{x}^\star$ such that the
expected simple regret under $p_N$ is minimized, i.e., $\mathbf{\tilde x}_N = \arg\min_\mathbf{x}
\text{ER}(p_N)(\mathbf{x})$.
The minimizer $\mathbf{\tilde x}_N$ of the expected simple regret under fixed
$p(f)$ can be approximated efficiently in the case of a GP since it is
identical to the maximizer of the GP's mean $\mu_N(\mathbf{x})$.

>>>>

\subsection{Formulation}
Let $\mathcal{X} \subset \mathcal{R}^D$ be some bounded domain and $f: \mathcal{X} \mapsto
\mathbb{R}$ be a function. We are interested in finding the maximum
$\mathbf{x}^\star$ of $f$ on $\mathcal{X}$. Let there be a probability measure
$p(f)$ over the space of functions $f: \mathcal{X} \mapsto \mathbb{R}$, such as
a GP. Based on this $p(f)$, we would ultimately like to
select an $\mathbf{\tilde x}$ which has minimum simple regret
$R_f(\mathbf{\tilde x})$. We define the expected simple regret ER of
selecting parameter $\mathbf{x}$ under $p(f)$ as:
$$\text{ER}(p)(\mathbf{x}) = \mathbb{E}_{p(f)}[R_f(\mathbf{x})]
= \mathbb{E}_{p(f)}[\max_{\mathbf{x}} f(\mathbf{x}) - f(\mathbf{
x})]$$

In $N$-step Bayesian optimization, we are given a budget of $N$ function evaluations and are to choose a sequence of $N$ query points
$X^q_N=\{\mathbf{x}^q_1, \dots, \mathbf{x}^q_N\}$ for which we evaluate $y_i = f(\mathbf{x}^q_i) +
\epsilon$ to obtain $\mathcal{D}_N = \{\mathbf{x}^q_i, y_i\}_{i=1}^N$. Based on this, 
 $p_N(f) = p(f \vert \mathcal{D}_N)$ is estimated and a point
$\mathbf{\tilde x}_N$ is recommended as the estimate of $\mathbf{x}^\star$ such that the
expected simple regret under $p_N$ is minimized, i.e., $\mathbf{\tilde x}_N = \arg\min_\mathbf{x}
\text{ER}(p_N)(\mathbf{x})$.
The minimizer $\mathbf{\tilde x}_N$ of the expected simple regret under fixed
$p(f)$ can be approximated efficiently in the case of a GP since it is
identical to the maximizer of the GP's mean $\mu_N(\mathbf{x})$.
